Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-15 paper/paper.tex
intro pass

\usepackage{times}
\usepackage{complexity}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{xcolor,colortbl}
\usepackage{tabularx}
\usepackage{siunitx}
\usepackage{xspace}
\usepackage{scalefnt}
\usepackage{graphicx}
\usepackage{booktabs}

@@

\begin{abstract}
Subgraph isomorphism is a computationally challenging problem with important practical
applications, for example in computer vision, biochemistry, and model checking. There are a number
of state-of-the-art algorithms for solving the problem, each of which has its own performance
characteristics. As with many other hard problems, the single best choice of algorithm overall is
rarely the best algorithm on an instance-by-instance. We develop a portfolio approach which leverages
novel features to characterise subgraph isomorphism problems to dynamically decide which algorithm
to use on a per-instance basis. We demonstrate significant performance improvements on a large set
of hard benchmark problems. In addition, we show how algorithm selection models can be leveraged to
gain new insights into what affects the performance of an algorithm.
\end{abstract}

@@

The subgraph isomorphism problem is to find an adjacency-preserving injective mapping from vertices
of a small \emph{pattern} graph to vertices of a large \emph{target} graph. This \NP-complete
problem has many important practical applications, for example in computer vision
\cite{cviu11,pr15}, biochemistry \cite{Giugno:2013}, and model checking \cite{Sevegnani:2015}. There
exist various exact algorithms, which have been compared on a large suite of problem instances by
McCreesh and Prosser \cite{McCreesh:2015}. These experiments indicated that the single best
algorithm depends on the CPU time limit considered: for very small CPU time limits, \VFtwo
\cite{Cordella:2004} is the best choice, whereas the \Glasgow algorithm \cite{McCreesh:2015} has
better success rates for larger time limits.  They also showed that on an instance by instance
basis, other algorithms are often better. This motivates us for introducing and evaluating a per-instance algorithm selection  approach for this problem.

The per-instance algorithm selection problem~\cite{rice_algorithm_1976} is to select from an
algorithm portfolio~\cite{huberman_economics_1997,gomes_algorithm_2001} the one expected to perform
best on a given problem instance. Algorithm selection systems usually build machine learning models
of the algorithms or the in which portfolio they are contained to forecast which algorithm to use in a
particular context. Using the model predictions, one or more algorithms from the portfolio are
selected to be run sequentially or in parallel.

@@

\paragraph{Overview of the paper.}
We formally define the subgraph isomorphism problem in Section 2. 
In Section 3, we describe the main existing algorithms for solving this problem, and we also introduce two new algorithms which are derived from the LAD algorithm of \cite{Solnon:2010}.

In Section 4, we experimentally compare some algorithms. We describe a large benchmark composed of 5725 instances grouped into 12 classes: 10 of these classes have already been used in the experimental study reported in  \cite{McCreesh:2015}, and 2 are new ones. We evaluate 8 algorithms on this benchmark (6 existing algorithms, and our 2 new algorithms), and we show that they have very compementary performance. In particular, we show that 4 of these algorithms are single best algorithms, depending on the CPU time limit considered.

In Section 5, we describe the features that are used to describe instances, and we describe our algorithm selection approach. It combines a presolving step, which allows us to very quickly solve easy instances, with the algorithm selection approach \LLAMA~\cite{kotthoff_llama_2013}.

In Section 6, we experimentally evaluate our selection approach, and show that it is able to close almost 70\% of the gap between the single best and the virtual best solver.

\section{Definitions and Notations}

@@

\section{Subgraph Isomorphism Algorithms}

@@

\section{Experimental Comparison of Individual Algorithms}

@@

\section{Algorithm Selection Approach}

@@

\section{Experimental Evaluation of Algorithm Selection}

@@

\section{Conclusion and Future Work}

>>>>

\usepackage{times}
\usepackage{complexity}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{xcolor,colortbl}
\usepackage{tabularx}
\usepackage{siunitx}
\usepackage{xspace}
\usepackage{scalefnt}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[sort]{cite}

@@

\begin{abstract}
Subgraph isomorphism is a computationally challenging problem with important practical
applications, for example in computer vision, biochemistry, and model checking. There are a number
of state-of-the-art algorithms for solving the problem, each of which has its own performance
characteristics. As with many other hard problems, the single best choice of algorithm overall is
rarely the best algorithm on an instance-by-instance. We develop a portfolio approach which leverages
novel features to characterise subgraph isomorphism problems to dynamically decide which algorithm
to use on a per-instance basis. We demonstrate substantial performance improvements on a large set
of hard benchmark problems. In addition, we show how algorithm selection models can be leveraged to
gain new insights into what affects the performance of an algorithm.
\end{abstract}

@@

The subgraph isomorphism problem is to find an adjacency-preserving injective mapping from vertices
of a small \emph{pattern} graph to vertices of a large \emph{target} graph. This \NP-complete
problem has many important practical applications, for example in computer vision
\cite{cviu11,pr15}, biochemistry \cite{Giugno:2013}, and model checking \cite{Sevegnani:2015}. There
exist various exact algorithms, which have been compared on a large suite of problem instances by
McCreesh and Prosser \cite{McCreesh:2015}. These experiments indicated that the single best
algorithm depends on the CPU time limit considered: for very small CPU time limits, \VFtwo
\cite{Cordella:2004} is the best choice, whereas the \Glasgow algorithm \cite{McCreesh:2015} has
better success rates for larger time limits.  They also showed that on an instance by instance
basis, other algorithms are often better.

The per-instance algorithm selection problem~\cite{rice_algorithm_1976} is to select from an
algorithm portfolio~\cite{huberman_economics_1997,gomes_algorithm_2001} the
algorithm expected to perform
best on a given problem instance. Algorithm selection systems usually build machine learning models
of the algorithms or the portfolio which they are contained in to forecast which algorithm to use in a
particular context. Using the predictions, one or more algorithms from the
portfolio can be selected to be run sequentially or in parallel.

@@

\paragraph{Overview of the paper.}
We formally define the subgraph isomorphism problem in Section~\ref{sec:defs}. 
In Section~\ref{sec:algs}, we describe the main existing algorithms for solving this problem, and we also introduce two new algorithms which are derived from the LAD algorithm of \cite{Solnon:2010}.

In Section~\ref{sec:algs}, we experimentally compare eight state-of-the-art
algorithms. We introduce a large benchmark set composed of 5725 instances
composed of twelve classes. Ten of these classes have been introduced in the
experimental study reported in~\cite{McCreesh:2015}. We evaluate the algorithms,
of which two are novel, on this benchmark set, and show that they have very
complementary performance. In particular, we show that depending on the CPU time
limit, different algorithms achieve the best performance on the entire benchmark
set.

In Section~\ref{sec:algsel}, we describe the features that are used to describe instances, and we describe our algorithm selection approach. It combines a presolving step, which allows us to very quickly solve easy instances, with the algorithm selection approach \LLAMA~\cite{kotthoff_llama_2013}.

In Section~\ref{sec:algsel-exps}, we experimentally evaluate our selection
approach, and show that it is able to close almost 70\% of the gap between the
single best and the virtual best solver.

We conclude and give directions for future work in Section~\ref{sec:concs}.

\section{Definitions and Notations}\label{sec:defs}

@@

\section{Subgraph Isomorphism Algorithms}\label{sec:algs}

@@

\section{Experimental Comparison of Individual Algorithms}\label{sec:exps}

@@

\section{Algorithm Selection Approach}\label{sec:algsel}

@@

\section{Experimental Evaluation of Algorithm Selection}\label{sec:algsel-exps}

@@

\section{Conclusion and Future Work}\label{sec:concs}
